A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-26 tex-arxiv/article.tex
add model count and type description to results

\begin{table}
	\caption{Model hyperparameters}
	\centering
	\begin{tabular}{lll}
		\toprule
		Parameter & Feedforward & RNN \\
		\midrule
		Architecture & 2 fully-connected hidden layers, ReLU  & GRU, fully connected linear output   \\
		Parameter counts     & 128-1024 perceptrons per layer & 128-512 perceptrons \\
		Training epochs     & 20-100       & 300-1200  \\
		Batch size    & 64       & 32  \\
		Optimizer    & \multicolumn{2}{c}{Adam}  \\
		Learning rate    & $10^{-4}$       & $10^{-3}, 10^{-4}$   \\
		\bottomrule
	\end{tabular}
	\label{tab:table1}
\end{table}

@@

As illustrated in fig. \ref{fig:vis_exec}, in terms of the qualitative aspects of executing a throw a successful result was attained with several models. Trajectories that visually resemble throwing motions were produced, and, when used to produce motion plans for a \emph{Universal Robotics Ur5e} robot equipped with a pneumatic gripper, they were adequate for throwing a plastic bottle into a target container located outside the robot's range of motion. Adequate output sequences were attained with both model architectures at multiple hyperparameter combinations, so to draw specific conclusions we need to look at the quantitative indicators of performance discussed above.

Figure \ref{fig:res_model_compare} shows a broad comparison between the RNN and feedforward model architectures, with each of the evaluation metric classes being present. In terms of distribution similarity measures like cosine similarity and Euclidean distance, the results are generally quite good for both models, with the RNN having the edge in most distance measures but notably one of the feedforward models demonstrating the highest cosine similarity. In terms of step-wise metrics, RNN models are typically better. The same is true for the throw error metric in general, but the best single result was attained by a feedforward model -- an average error of around 9cm, as opposed to around 11.5cm for the best recurrent model.

@@

@@

bla bla bla

>>>>

\begin{table}
	\caption{Model hyperparameters}
	\centering
	\begin{tabular}{lll}
		\toprule
		Parameter & Feedforward & RNN \\
		\midrule
		Architecture & 2 fully-connected hidden layers, ReLU  & GRU, fully connected linear output   \\
		Parameter counts     & 128-1024 perceptrons per layer & 128-512 perceptrons in the unit \\
		Training epochs     & 20-100       & 300-1200  \\
		Batch size    & 64       & 32  \\
		Optimizer    & \multicolumn{2}{c}{Adam}  \\
		Learning rate    & $10^{-4}$       & $10^{-3}, 10^{-4}$   \\
		\bottomrule
	\end{tabular}
	\label{tab:table1}
\end{table}

@@

Over the course of our research, numerous models were trained on both of the data sets described in \ref{sec:collection}, in both of the architectures discussed in \ref{sec:models}. After the initial trial and error process, a systematic training regimen produced the following:

\begin{itemize}
	\item feedforward networks -- a total of 48 models, varying the training data set, presence of a time signal in the features, perceptron counts per hidden layer and training duration;
	\item RNNs -- 36 models with data set, learning rate, model size and training length being the variable parameters.
\end{itemize}

As illustrated in fig. \ref{fig:vis_exec}, model outputs were visualized to use their qualitative aspects in guiding hyperparameter choice and a preliminary implementation on a real robot was also achieved -- executing throws with some sampled trajectories generated by the simpler feedforward network. As can be seen, when these outputs were used to generate motion plans for a \emph{Universal Robotics Ur5e} robot equipped with a pneumatic gripper, a plastic bottle was successfully thrown into a target container located outside the robot's reachable volume. Adequate output sequences were attained with both model architectures at multiple hyperparameter combinations, so to draw specific conclusions the quantitative evaluation metrics discussed in \ref{sec:eval} were computed on the 84 systematically trained models described above.

@@

Figure \ref{fig:res_model_compare} shows a broad comparison between the RNN and feedforward model architectures, with each of the evaluation metric classes being present, though not all the specific metrics discussed -- as there was found to be a considerable amount of duplication in their findings.

@@

In terms of distribution similarity measures such as cosine similarity and Euclidean distance, the results are generally quite good for both models, with the RNN having the edge in most distance measures but notably one of the feedforward models demonstrating the highest cosine similarity. In terms of step-wise metrics, RNN models are typically better. The same is true for the throw error metric in general, but the best single result was attained by a feedforward model -- an average error of around 9cm, as opposed to around 11.5cm for the best recurrent model.
